NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-12 paper/main.tex
BMI table hypertension results added
BMI table 2 done
results almost done
results checked again
introduction done

%\usepackage[table]{xcolor}
\usepackage{colortbl} % to use colors for tables
\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
\usepackage{caption} % to change the font of the table titles
\usepackage{amssymb} % to use \leqslant
\usepackage[clockwise]{rotating} % to rotate pages for wide tables
%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

\setlength{\parindent}{0pt}

@@

\noindent Signed:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date:\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents

I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr. Suzana Almoosawi for her invaluable nutritional academic insight, and suggestions. \\

@@

I also want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\end{abbreviations}

@@

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters

\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
%\include{Chapters/Chapter5}

>>>>

%\usepackage[table]{xcolor}
\usepackage{colortbl} % to use colors for tables
\usepackage[usestackEOL]{stackengine} %to change lines within a cell in the table
\usepackage{caption} % to change the font of the table titles
\usepackage{amssymb} % to use \leqslant
\usepackage[clockwise]{rotating} % to rotate pages for wide tables
%\usepackage{pdflscape} % to rotate page into landscape
%\usepackage[paper = {portrait or landscape}, page size]{typearea}

%----------------------------------------------------------------------------------------
%	MARGIN SETTINGS
%----------------------------------------------------------------------------------------

@@

{\parindent}{0pt}

@@

\noindent Signed: \;\;\;\;\;\;\includegraphics[height=2.5\baselineskip]{Figures/signature.png}\\
\rule[0.5em]{25em}{0.5pt} % This prints a line for the signature

\noindent Date: \;\;\;\;\;\;\;\;\;\;\;\;2018-09-05\\
\rule[0.5em]{25em}{0.5pt} % This prints a line to write the date
\end{declaration}

@@

\begin{acknowledgements}
\addchaptertocentry{\acknowledgementname} % Add the acknowledgements to the table of contents
\vspace{0.8cm}
I would like to thank my tutor and supervisor \supname, for his guidance, patience, and help while working on this project and also to Dr. Suzana Almoosawi for her invaluable nutritional academic insight, and suggestions. \\

@@

%I would also like to thank Aichi Medical Univeristy, and Egashira Hospitality Public Interest Foundation for funding my studentship at the London School of Hygiene and Tropical Medicine. \\

Last but not the least, I want to express my gratitude to my family for their unconditional support, understanding, and encouragement throughout this year. \\

@@

\textbf{AIC} & \textbf{A}kaike \textbf{I}information \textbf{C}riterion \\
\textbf{A1c} & Haemoglobin \textbf{A1c}: Glycated hemoglobin \\
%\textbf{aBIC} & \textbf{a}djusted \textbf{B}ayesian \textbf{I}nformation \textbf{C}riterion \\
\textbf{BMI} & \textbf{B}ody \textbf{M}ass \textbf{I}ndex \\
%\textbf{cAIC} & \textbf{c}onsistent \textbf{A}kaike \textbf{I}nformation \textbf{C}riterion \\
\textbf{BIC} & \textbf{B}ayesian \textbf{I}information \textbf{C}riterion \\
\textbf{CI}  & \textbf{C}onfidence \textbf{I}nterval \\
\textbf{DM}  & \textbf{D}iabetes \textbf{M}ellitus \\
\textbf{EM}  & \textbf{E}xpectation \textbf{M}aximazation  \\
\textbf{FSA} & \textbf{F}ood \textbf{S}tandards \textbf{A}gency  \\
\textbf{HDL} & \textbf{H}igh \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LDL} & \textbf{L}ow \textbf{D}ensity \textbf{L}ipoprotein cholesterol \\
\textbf{LCA} & \textbf{L}atent \textbf{C}lass \textbf{A}nalysis\\
%\textbf{LCGA} & \textbf{L}atent \textbf{C}lass \textbf{G}rowth \textbf{A}nalysis \\
%\textbf{LTA} & \textbf{L}atent \textbf{T}ransition \textbf{A}nalysis \\
\textbf{MAFF} & \textbf{M}inistry of \textbf{A}griculture, \textbf{F}isheries and \textbf{F}ood \\
%\textbf{MAR} & \textbf{M}issing \textbf{A}t \textbf{R}andom \\
%\textbf{MCAR} & \textbf{M}issing \textbf{C}ompletely \textbf{A}t \textbf{R}andom \\
\textbf{MLCA} & \textbf{M}ultilevel \textbf{L}atent \textbf{C}lass \textbf{A}nalysis \\
%\textbf{MNAR} & \textbf{M}issing \textbf{N}ot \textbf{A}t \textbf{R}andom \\
\textbf{ML} & \textbf{M}aximum \textbf{L}ikelihood \\
\textbf{NDNS} & the \textbf{N}ational \textbf{D}ietary and \textbf{N}utrition \textbf{S}urvey \\
\textbf{OR} & \textbf{O}dds \textbf{R}atio \\
\textbf{PHE} & \textbf{P}ublic \textbf{H}ealth \textbf{E}ngland  \\
\textbf{PSUs} & \textbf{P}rimary \textbf{S}ampling \textbf{U}nits \\
\textbf{TC} & \textbf{T}otal \textbf{C}holesterol \\
\textbf{TG} & \textbf{T}ri\textbf{g}lycerides \\
\textbf{WC}   & \textbf{W}aist \textbf{C}ircumference \\
\end{abbreviations}

@@

% Include the chapters of the thesis as separate files from the Chapters folder
% Uncomment the lines as you write the chapters
\linespread{1.25}
\include{Chapters/Chapter1}
\include{Chapters/Chapter2}
\include{Chapters/Chapter3}
\include{Chapters/Chapter4}
%\include{Chapters/Chapter5}
